Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-13 paper/paper.tex
Jesse revisions to PacBio methods

\figdata{textfile providing all primer sequences used to amplify and enrich influenza transcripts for PacBio sequencing. \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/WorkflowSchematic/PacBio_primer_list.txt} 
}
\label{figdata:primer_sequences}

@@

%%% start genotypes figure %%%
\begin{figure}
\begin{fullwidth}
{\centering
\includegraphics[height=0.8\textheight]{figures/single_cell_figures/p_genotypes.pdf}
}
\caption{
Viral genotypes and infection outcomes in single cells.
Each row shows a single infected cell.
Arrows indicate the presence of a viral gene from a single viral barcode variant (light blue) or both barcode variants (dark blue).
Circles and boxes indicate mutations or indels as described in the legend.
Circle areas and box heights are proportional to the fraction of PacBio CCSs that report the mutation (see \FIGDATA[genotypes]{genotypes} for numerical data).
For dual-barcode infections, mutations / indels for the wildtype viral variant are on the top half of the arrow and those for the synonymously barcoded variant are on the bottom half. 
Green boxes to the left show the percent of all mRNA in that cell derived from virus.
Orange boxes show the percent of cellular mRNA derived from IFN, with boxes framed in orange indicating cells classified as IFN+ in \FIG{experiment}H.
}
\label{fig:genotypes}

@@

>>>>

@@

%%% start genotypes figure %%%
\begin{figure}
\begin{fullwidth}
{\centering
\includegraphics[height=0.76\textheight]{figures/single_cell_figures/p_genotypes.pdf}
}
\caption{
Viral genotypes and infection outcomes in single cells.
Each row shows a single infected cell.
Arrows indicate the presence of a viral gene from a single viral barcode variant (light blue) or both barcode variants (dark blue).
Circles and boxes indicate mutations or indels as described in the legend.
Circle areas and box heights are proportional to the fraction of PacBio CCSs that report the mutation (see \FIGDATA[genotypes]{genotypes} for numerical data).
For dual-barcode infections, mutations / indels for the wildtype viral variant are on the top half of the arrow and those for the synonymously barcoded variant are on the bottom half. 
Green boxes to the left show the percent of all mRNA in that cell derived from virus.
Orange boxes show the percent of cellular mRNA derived from IFN, with boxes framed in orange indicating cells classified as IFN+ in \FIG{experiment}H.
}
\label{fig:genotypes}

@@

\figdata{A text file giving the primers used to amplify the influenza transcripts for PacBio sequencing are at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/WorkflowSchematic/PacBio_primer_list.txt} 
}
\label{figdata:primer_sequences}
